---
title: "dfg-11"
author: "dfg-11"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning= FALSE, 
                      size = 'tiny')
```

```{r, echo = FALSE}
rm(list=ls())
library(MASS) #contains Boston data set
library(ISLR) #package to accompany the book
library(ggplot2) #fancy plots
library(knitr) #styling output 
# library(kableExtra) #styling tables output
library(readxl)#exel file
library(caret)#to split data into training and test sets
# library(tree)
library(dplyr) # for data manipulation

set.seed(321321)
```

```{r}
# data <- read_excel(file.path(getwd(), "config_files", "Goal4.xlsx"), 
#                    sheet = 1)

data = read.csv(file = file.path(getwd(), "cleaned_data.csv"))

# View(head(data))
```

Final data set for random forest model

Note that series description have been converted to numerical values
We need numerical values:
0 - Adjusted gender parity index for completion rate, by sex, location, wealth quintile and education level
1 - Adjusted location parity index for completion rate, by sex, location, wealth quintile and education level
2 - Adjusted wealth parity index for completion rate, by sex, location, wealth quintile and education level

We also need: 
- GeoAreaCode
- Time_Detail 
 

```{r}

variables = c("Value", "GeoAreaCode", "Time_Detail", "SeriesDescription")

data_subset = data %>% select(all_of(variables))

```

Susbset into 2019 and non-2019 sets
```{r}

data_1 = data_subset[data_subset$Time_Detail == 2019,]

time_detail = c(2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018)

data_2 = data_subset[data_subset$Time_Detail != 2019,]
# View(data_2)
```

```{r}
split_index <- createDataPartition(data_2$Value, 
  p = .75, #the percentage of data that goes to training
  list = FALSE)#results returned as a matrix
data_train <- data_2[ split_index, ]
data_test <- data_2[-split_index, ]
```

```{r}
library(randomForest)
p <- (dim(data_2)[2] -1) #number of predictors
RF.fit <- randomForest(Value~., data = data_train, mtry = floor(sqrt(p)), importance = TRUE)
RF.fit
```










